|

### 2021-12-16 front-and-back-matter/_acknowledgements.Rmd
End of day:

I am extremely grateful to all those who contributed their time and energy to my research projects: Athena Sheppard, Emily Hennessy, Matthew Lee, Lena Schmidt, Alexandra McAleenan, Vincent Cheng, Francesca Spiga, Sarah Dawson and Rebecca Turner. A special mention goes to Mark Newbury of the Dementia Platform UK, who worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.

I also want to thank the many people who raised issues or otherwise provided feedback on the open source tools built as part of this thesis - it's been a joy to watch others build on my work. A special mention must go to Randall Boyes and Alex J Fowler for their input/work on the `robvis` tool.

@@

Ciara, I'd need (at least) another <<words>> words to accurately describe all the ways in which you supported me through this endeavour. It can't have been fun being locked-down in a small flat with a grumpy and stressed PhD student, nor trying to support the same student remotely from Dublin. In the Discussion, I talk about lessons learned during this thesis, but the biggest takeaway of this whole experience for me is that I am incredibly lucky to have found you and to get to take on life while holding your hand. Thank you and I love you.

>>>>

I am extremely grateful to all those who contributed their time and energy to my research projects: Athena Sheppard, Emily Hennessy, Matthew Lee, Lena Schmidt, Alexandra McAleenan, Vincent Cheng, Francesca Spiga, Sarah Dawson and Rebecca Turner. A special mention goes to Mark Newbury of the Dementia Platform UK, who supported my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.

I also want to thank the many people who raised issues or otherwise provided feedback on the open-source tools built as part of this thesis - it's been a joy to watch others build on my work. A special mention must go to Randall Boyes and Alex J Fowler for their input/work on the `robvis` tool.

@@

Ciara, I'd need (at least) another <<words>> words to accurately describe all the ways in which you supported me through this endeavour. It can't have been fun being locked down in a small flat with a grumpy and stressed PhD student, nor trying to support the same student remotely from Dublin. In the Discussion, I talk about lessons learned during this thesis, but the biggest takeaway of this whole experience for me is that I am incredibly lucky to have found you and to get to take on life while holding your hand. Thank you and I love you.

### 2021-12-16 index.Rmd
End of day:

<!--
Include the create_chunk_options chunk above at the top of your index.Rmd file
This will include code to create additional chunk options (e.g. for adding author references to savequotes)
If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
-->

>>>>

<!--
Include the create_chunk_options chunk above at the top of your index.Rmd file
This will include code to create additional chunk options (e.g., for adding author references to savequotes)
If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
-->

### 2021-12-16 reviews/year_2/report.Rmd
End of day:

This chapter introduces a tool built in R to allow for systematic searching of the [medRxiv](https://www.medrxiv.org/) and [bioRxiv](https://www.biorxiv.org/) preprint repositories. Preprints represent an important source of grey literature and so should be included as part of a systematic review. However, the native search interface on preprint websites do not allow for complex search strategies (e.g. those using Boolean operators or wildcards) and are not transparent or reproducible, with the same search producing wildly different numbers of records over time.

@@

This chapter will present the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/blood lipids interventions (e.g. statins) and dementia. The review included all types of study design including randomised controlled trials, Mendelian randomization analyses, and non-randomised studies of exposures and interventions (NRSI/NRSE).

@@

In terms of the meta-analysis of the non-intervention studies, this was complicated by the different ways in which lipid fractions were quantified in different studies (e.g. grouped based on clinical guidelines or quantiles, or dichotomized into a hypercholesterolemia variable). However, following discussion with my supervisors who pointed me towards useful material on this subject, this element of the analysis is almost complete.

@@

* _Comprehensiveness:_ While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g. ROBINS-I/E). This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
* _Inclusion of preprints:_ Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched  preprinted health-related manuscripts as a source of grey literature. As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.

@@

In terms of the broader thesis, while these concerns mean I have low confidence in the accuracy of the result, it presents a good opportunity for comparison with other published papers that used different analytical strategies where the source and direction of bias is different (e.g. confounding by indication in our analysis likely makes statin use look worse but immortal time bias in other papers likely makes statin use look better).

>>>>

This chapter introduces a tool built in R to allow for systematic searching of the [medRxiv](https://www.medrxiv.org/) and [bioRxiv](https://www.biorxiv.org/) preprint repositories. Preprints represent an important source of grey literature and so should be included as part of a systematic review. However, the native search interface on preprint websites do not allow for complex search strategies (e.g., those using Boolean operators or wildcards) and are not transparent or reproducible, with the same search producing wildly different numbers of records over time.

@@

This chapter will present the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/blood lipids interventions (e.g., statins) and dementia. The review included all types of study design including randomised controlled trials, Mendelian randomization analyses, and non-randomised studies of exposures and interventions (NRSI/NRSE).

@@

In terms of the meta-analysis of the non-intervention studies, this was complicated by the different ways in which lipid fractions were quantified in different studies (e.g., grouped based on clinical guidelines or quantiles, or dichotomized into a hypercholesterolemia variable). However, following discussion with my supervisors who pointed me towards useful material on this subject, this element of the analysis is almost complete.

@@

* _Comprehensiveness:_ While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g., ROBINS-I/E). This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
* _Inclusion of preprints:_ Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched  preprinted health-related manuscripts as a source of grey literature. As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.

@@

In terms of the broader thesis, while these concerns mean I have low confidence in the accuracy of the result, it presents a good opportunity for comparison with other published papers that used different analytical strategies where the source and direction of bias is different (e.g., confounding by indication in our analysis likely makes statin use look worse but immortal time bias in other papers likely makes statin use look better).
